The Astropy Project:

### 2017-09-29 main.tex
tweaks
note about abs

\begin{abstract}
The Astropy project supports and fosters the development of open-source Python
packages that provide commonly-needed functionality to the astronomical
community.
A key element of the project is the Astropy core package, which serves as the
foundation for more specialized projects and packages.
In this article, we provide an overview of the organization of the Astropy
project and summarize key features in the core package as of the recent major
release, version 2.0.
We then describe the project infrastructure designed to facilitate [...]
We conclude with a future outlook of planned new features and directions for the
broader Astropy ecosystem.
\end{abstract}

@@

Historically, it has been unusual to keep units as part of numbers, especially as speed was often deemed essential and quantities used to be slower than regular arrays. Hence, programs and functions expected to be fed parameters in particular units, as (hopefully) stated in their documentation.  In astropy 0.4, therefore, unit and quantity support was still somewhat spotty, but this has changed greatly.  One of the riskiest classes was ngles, where both degrees and radians were ``obvious'' default units to some. As a consequence, quantities are most fully integrated in the coordinates module (Sect.~\ref{sec:coordinates}). In astropy 2.0, one can also opt in to use quantities fully in tables, by using the {\tt QTable} class (see Sect.~\ref{sec:table}). As a result, units in fits tables are also well-supported. For most other modules, quantities are at least accepted, and often assumed by default.

@@

\subsubsection{Accuracy and comparison of coordinate system definitions?}
% Erik?

@@

Explain components: Documentation, Example gallery, Tutorials and lessons

>>>>

\begin{abstract}
% I (Adrian) took a first stab at the abstract, but it needs some work. Feel
% free to modify!
The Astropy project supports and fosters the development of open-source Python
packages that provide commonly-needed functionality to the astronomical
community.
A key element of the project is the Astropy core package, which serves as the
foundation for more specialized projects and packages.
In this article, we provide an overview of the organization of the Astropy
project and summarize key features in the core package as of the recent major
release, version 2.0.
We then describe the project infrastructure designed to facilitate [...]
We conclude with a future outlook of planned new features and directions for the
broader Astropy ecosystem.
\end{abstract}

@@

Historically, it has been unusual to keep units as part of numbers, especially as speed was often deemed essential and quantities used to be slower than regular arrays. Hence, programs and functions expected to be fed parameters in particular units, as (hopefully) stated in their documentation.  In astropy 0.4, therefore, unit and quantity support was still somewhat spotty, but this has changed greatly.  One of the riskiest classes was ngles, where both degrees and radians were ``obvious'' default units to some. As a consequence, quantities are most fully integrated in the coordinates module (\sectionname~\ref{sec:coordinates}). In astropy 2.0, one can also opt in to use quantities fully in tables, by using the {\tt QTable} class (see \sectionname~\ref{sec:table}). As a result, units in fits tables are also well-supported. For most other modules, quantities are at least accepted, and often assumed by default.

@@

\subsubsection{Accuracy and comparison of coordinate system definitions}
% Erik?

@@

Explain components: Documentation, Tutorials, and lessons
